### 2013-09-05 Tex/chapters/results.tex
Formulierung hoffentlich klarer

            \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
            {
                Top: Critical Temperature \(T_c\) of the graph over different
                disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Bottom: Critical temperatures normalized by degree \(K\) over
                different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG. The values of \(T_c / K\)
                are compared to those of \(T_c /  \avg{\sum_{\avg{i,j}}J_{ij}}\)
                from Sec.\ \ref{sssec:J}.
            }
            \label{fig:Tc_deg_A0}
        \end{figure}\\
        Because Ref.\ \cite{Janke1994} gives for the DT with \(J=1\) a
        critical temperature of \(T_{c,DT} = 3.80\)\footnote{more precise: a value of \(\frac{1}{T_c} \approx 0.263\) is given},
        it can be compared to the obtained \(T_{c,GG} = 2.19\)
        and \(T_{c,RNG} = 1.13\) for \(\sigma = 1.2\), which should be very
        similar to a Poisson distributed set of nodes.
        Note that while for the graph ensembles as mentioned in Sec. \ref{ssec:graphtypes}
        the relation
        \begin{equation}
            DT \supseteq GG \supseteq RNG
        \end{equation}
        holds, also the
        relation
        \begin{equation}
            T_{c,DT} \ge T_{c,GG} \ge T_{c,RNG}
        \end{equation}
        holds.
        Also keep in mind that the relation \(T_{c,GG} \ge T_{c,RNG}\)
        was true for \(\alpha = 0.5\) in the preceding sections.
        This phenomenon is also known from percolation where the relation
        \(p_{c,DT} \ge p_{c,GG} \ge p_{c,RNG}\) holds for the percolation
        threshold \(p_c\) -- the critical point of the percolation problem.
        That the subgraph hierachy can be translated to
        the sequence of \(p_c\) for the subgraphs, is known as the containment
        theorem \cite{fisher}.
        Possibly the containment theorem is also applicable on this kind of
        problem.

>>>>

            \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
            {
                Top: Critical Temperature \(T_c\) of the graph over different
                disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Bottom: Critical temperatures normalized by degree \(K\) over
                different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG. The values of \(T_c / K\)
                are compared to those of \(T_c /  \avg{\sum_{\avg{i,j}}J_{ij}}\)
                from Sec.\ \ref{sssec:J}.
            }
            \label{fig:Tc_deg_A0}
        \end{figure}\\
        Because Ref.\ \cite{Janke1994} gives for the DT with \(J=1\) a
        critical temperature of \(T_{c,DT} = 3.80\)\footnote{more precise: a value of \(\frac{1}{T_c} \approx 0.263\) is given},
        it can be compared to the obtained \(T_{c,GG} = 2.19\)
        and \(T_{c,RNG} = 1.13\) for \(\sigma = 1.2\), which should be very
        similar to a Poisson distributed set of nodes.
        Note that while for the graph ensembles the relation
        \begin{equation}
            DT \supseteq GG \supseteq RNG
        \end{equation}
        holds (see Sec. \ref{ssec:graphtypes}), the relation for the
        critical points on these graphs
        \begin{equation}
            T_{c,DT} \ge T_{c,GG} \ge T_{c,RNG}
        \end{equation}
        is also true.
        Also keep in mind that the relation \(T_{c,GG} \ge T_{c,RNG}\)
        was true for \(\alpha = 0.5\) in the preceding sections.
        This phenomenon is also known from percolation where the relation
        \(p_{c,DT} \ge p_{c,GG} \ge p_{c,RNG}\) holds for the percolation
        threshold \(p_c\) -- the critical point of the percolation problem.
        The fact that the subgraph hierachy can be translated to
        the sequence of \(p_c\) for the subgraphs, is known as the containment
        theorem \cite{fisher}.
        Possibly the containment theorem is also applicable on this kind of
        problem.
